Shap-based Average Treatment Effect Calculations

### 2019-03-11 Paper/main.tex
Updates from Overleaf

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}

@@

Under the strong ignorability assumption and equations from the Kang-Schafer paper we can compute the true ATT using the following steps:
\begin{equation*}
    \begin{split}
        ATT = & \mathbb{E}[Y_1 | X=x, T=1] - \mathbb{E}[Y_0 | X=x, T=1] \\
        \mathbb{E}[Y_1|T=1, X=x] = & \mathbb{E}[Y|T=1, X=x] \\
        \mathbb{E}[Y_0|T=1, X=x] = & \mathbb{E}[Y_0|T=0, X=x] = \mathbb{E}[Y|T=0, X=x] \\
    \end{split}
\end{equation*}
Therefore $ATT=\mu{}^{(1)} - \mu{}^{(0)} = 200-220 = -20$ 
%TODO: is this not actually 20?

\subsubsection{Z-Bias}

The Z-Bias generation process \cite{myers2011effects}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

@@

Under the strong ignorability assumption and equations from the Kang-Schafer paper we can compute the true ATT using the following steps:
\begin{equation*}
    \begin{split}
        ATT = & \mathbb{E}[Y_1 | X=x, T=1] - \mathbb{E}[Y_0 | X=x, T=1] \\
        \mathbb{E}[Y_1|T=1, X=x] = & \mathbb{E}[Y|T=1, X=x] \\
        \mathbb{E}[Y_0|T=1, X=x] = & \mathbb{E}[Y_0|T=0, X=x] = \mathbb{E}[Y|T=0, X=x] \\
    \end{split}
\end{equation*}
Therefore $ATT=\mu{}^{(1)} - \mu{}^{(0)} = 200-220 = -20$ 
%TODO: is this actually -20?

\subsubsection{Z-Bias}
Our second method of simulation is based on adjusting for instrumental biases. We implemented two types of simulations according to the Z-Bias generation process as described in Myers \textit{et al} \cite{myers2011effects}.

The simulation creates examples where there are: one instrumental variable $Z$, one unobserved variable affecting both treatment and outcome $U$, a treatment $X$ and an outcome $Y$. All four variables are binary. These are all described in figure \ref{fig:z_bias_explanation} from the original paper.

\begin{figure}
    \centering
    \includegraphics{Paper/images/z_bias_schema.png}
    \caption{A figure from Myers \textit{et al} depicting the relationships between variables in simulated data.}
    \label{fig:z_bias_explanation}
\end{figure}

There are two methods of simulation we use, an additive and a multiplicative version. In both versions the order of variables simulated is consistent in order to ensure that the risk of outcome would depend directly on $U$ and $X$ and indirectly on $Z$.

In the additive version of the simulation the first variable to be simulated is $Z$ that is created with the probability $P(Z=1)=0.5$.
Next the unobserved variable is simulated so that $P(U=1|Z)=\gamma{}_0 + \gamma{}_1\cdot{}Z$. Next the treatment is simulation using $P(X=1|U,Z) = \alpha{}_0 + \alpha{}_1 \cdot{} U + \alpha{}_2 \cdot{} Z$. Last we simulate the outcome using $P(Y=1|X,U) = \beta{}_0 + \beta{}_1 \cdot{} U + \beta{}_2 \cdot{} U$
